Exploratory Analysis Project 1
========================================================

This assignment uses data from the UC Irvine Machine Learning Repository, a popular repository for machine learning datasets. In particular, we will be using the "Individual household electric power consumption Data Set" which I have made available on the course web site:

Dataset: <a href="https://d396qusza40orc.cloudfront.net/exdata%2Fdata%2Fhousehold_power_consumption.zip">Electric power consumption [20Mb]</a>

The sqldf Package is required.

Description: Measurements of electric power consumption in one household with a one-minute sampling rate over a period of almost 4 years. Different electrical quantities and some sub-metering values are available.

The following descriptions of the 9 variables in the dataset are taken from the UCI web site:

1. Date: Date in format dd/mm/yyyy
2. Time: time in format hh:mm:ss
3. Global_active_power: household global minute-averaged active power (in kilowatt)
4. Global_reactive_power: household global minute-averaged reactive power (in kilowatt)
5. Voltage: minute-averaged voltage (in volt)
6. Global_intensity: household global minute-averaged current intensity (in ampere)
7. Sub_metering_1: energy sub-metering No. 1 (in watt-hour of active energy). It corresponds to the kitchen, containing mainly a dishwasher, an oven and a microwave (hot plates are not electric but gas powered).
8. Sub_metering_2: energy sub-metering No. 2 (in watt-hour of active energy). It corresponds to the laundry room, containing a washing-machine, a tumble-drier, a refrigerator and a light.
9. Sub_metering_3: energy sub-metering No. 3 (in watt-hour of active energy). It corresponds to an electric water-heater and an air-conditioner.

```{r}
library(sqldf)
data <- read.csv.sql(unzip("exdata-data-household_power_consumption.zip", "household_power_consumption.txt"), sql = "select * from file where Date = '1/2/2007' OR Date = '2/2/2007' ", sep=";", header=TRUE)
data$Date <- as.POSIXct(paste(as.character(data$Date), as.character(data$Time)), format="%d/%m/%Y %H:%M:%S")
head(data)
```

You can also embed plots, for example:

```{r fig.width=7, fig.height=6}
hist(data$Global_active_power, main="Global Active Power", xlab="Global Active Power (kilowatts)", col="red")
```

```{r fig.width=7, fig.height=6}
plot(data$Date, data$Global_active_power, main="", xlab="", ylab="Global Active Power (kilowatts)", pch=NA)
lines(data$Date, data$Global_active_power)
```

```{r}
y = cbind(data$Sub_metering_1, data$Sub_metering_2, data$Sub_metering_3)
x = data$Date
lower <- min(data$Date)
upper <- max(data$Date)
```

```{r fig.width=7, fig.height=6}
plot(data$Date,data$Sub_metering_1, pch=NA, xlab=NA, ylab="Energy sub metering")
lines(data$Date, data$Sub_metering_1)
lines(data$Date, data$Sub_metering_2, col="red")
lines(data$Date, data$Sub_metering_3, col="blue")
##axis(1, at=seq(lower,upper,86400), label=T, tick=T)
legend("topright", c("Sub Metering 1", "Sub Metering 2", "Sub Metering 3"), col=c("black", "red", "blue"), lty=c(1,1,1), pch=c(NA,NA,NA))
```

```{r fig.width=7, fig.height=7}
par(mfrow = c(2,2))



plot(data$Date, data$Global_active_power, main="", xlab="", ylab="Global Active Power (kilowatts)", pch=NA)
lines(data$Date, data$Global_active_power)

plot(data$Date, data$Voltage, main="", xlab="datetime", ylab="Voltage", pch=NA)
lines(data$Date, data$Voltage)

plot(data$Date,data$Sub_metering_1, pch=NA, xlab=NA, ylab="Energy sub metering")
lines(data$Date, data$Sub_metering_1)
lines(data$Date, data$Sub_metering_2, col="red")
lines(data$Date, data$Sub_metering_3, col="blue")

legend("topright", c("Sub Metering 1", "Sub Metering 2", "Sub Metering 3"), col=c("black", "red", "blue"), lty=c(1,1,1), pch=c(NA,NA,NA), bty="n", inset=0.05)

plot(data$Date, data$Global_reactive_power, main="", xlab="datetime", ylab="Global Reactive Power", pch=NA)
lines(data$Date, data$Global_reactive_power)
```